A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-08-03 paper/elsarticle/elsarticle-template.tex
paper

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp the images to be projected in a manner that they appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), this can be done in a cumbersome manual process called keystone correction---often using software bundled with the projector---to compute an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, by using a projector equipped with a steerable mirror and a camera facing the scene plane. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) placement of the desired augmentations is carried out in accordance with the axes of an image of the scene acquired by the camera, thereby making setting those axes as simple as appropriately rotating the camera. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby allowing for consistent scaling across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity vector, which they use to carry out a rotational correction in projecting to a wall. Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp.

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.3cm]{images/system2.png}}}
    \quad
    \subfloat[\centering Example projection of image warped for target location using our approach.]{{\includegraphics[height=3.3cm]{images/hans_undist.png}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a Panasonic PT-RZ660BE projector, a steerable mirror system manufactured by Dynamic Projection Institute, and a Stereolabs Zed 2 stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of our 15 target locations---an image warped using our approach, as seen from the downwards-facing camera. Note that the warp places the axes of the augmentation in accordance with the axes of the camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). Corners of the full projected image extent projected to the floor in light green.}
    \label{fig:eval}
\end{figure}

@@

\paragraph{Manual approach} Having pointed the steerable mirror to the desired location, manual keystone correction using the MDC-X software involves warping the image to be projected by manipulating the corners of the image until the desired effect is produced on the projection surface. In order to provide a template for manually carrying out keystone correction, we prepared a 50~cm~$\times$~31.25~cm piece of cardboard. For each target location, we placed this piece of cardboard in a manner that its axes were aligned with the principal axes of the scene (cf.\ the yellow and red lines in Figure \ref{fig:eval}(b)); we then manually warped the image for the given target location so that any corner of the augmentation deviated by at most 1 cm from the corresponding corner of the template. End-to-end, the process of setting the presets in the MDC-X software having carried out keystone correction manually took ca.\ 32 min for the 15 target locations.

@@

A natural extension of this work would be to address non-planar scenes. To handle non-planar scenes would call for a change in how scene geometry is recovered and how warping of the image to be projected is carried out; the methodology we proposed for projector calibration could, however, be left unchanged.

>>>>

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp an image to be projected in a manner that it, when projected, appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), a cumbersome manual process called keystone correction---often using software bundled with the projector---can be used to carry out an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, using a projector equipped with a steerable mirror and a camera facing the scene plane. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) placement of the desired augmentations is carried out in accordance with the axes of an image of the scene acquired by the camera, thereby making setting those axes as simple as appropriately rotating the camera. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby allowing for consistent scaling across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity vector, which they use to carry out a rotational correction in projecting to a wall. Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp, taking into account both desired in-plane orientation and metric scale.

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.3cm]{images/system2.png}}}
    \quad
    \subfloat[\centering Example projection of image warped for target location using our approach.]{{\includegraphics[height=3.3cm]{images/hans_undist_inset.png}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a Panasonic PT-RZ660BE projector, a steerable mirror system manufactured by Dynamic Projection Institute, and a Stereolabs Zed 2 stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of our 15 target locations---an image warped using our approach, as seen from the downwards-facing camera. Note that the warp places the axes of the augmentation in accordance with the axes of the camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). Corners of the full projected image extent projected to the floor in light green.}
    \label{fig:eval}
\end{figure}

@@

\paragraph{Manual approach} Having pointed the steerable mirror to the desired location, manual keystone correction using the MDC-X software involves warping the image to be projected by manipulating the corners of the image until the desired effect is produced on the projection surface. In order to provide a template for manually carrying out keystone correction, we prepared a rectangular 50~cm~$\times$~31.25~cm cutout of cardboard. For each target location, we placed this piece of cardboard in a manner that its axes were aligned with the principal axes of the scene (cf.\ the yellow and red lines in Figure \ref{fig:eval}(b)); we then manually warped the image for the given target location so that any corner of the augmentation deviated by at most 1 cm from the corresponding corner of the template. End-to-end, the process of setting the presets in the MDC-X software having carried out keystone correction manually took ca.\ 32 min for the 15 target locations.

@@

A natural extension of this work would be to address the augmentation of non-planar scenes. To handle non-planar scenes would call for a change in how scene geometry is recovered and how warping of the image to be projected is carried out; the methodology we proposed for projector calibration could, however, be left unchanged.
